Sound Synthesis

### 2020-10-07 Text/old/00Preambulo/Thesis.tex
organized text division

\input{00_Include.tex}
\usepackage[portuguese]{babel}

@@

\section{Introduction}
% Tell the reader the problem you are tackling in this project.

Humans are a creative bunch. Since the beginning of computing, even when mainframes were the only available medium, restricted to organizations with huge budgets, people found ways to develop artistic applications, like proto video games, in their (and the machine's) spare time. % TODO find citation

Music, on the other hand, is another staple of humanity's creativity. % TODO first musical instruments
 Is only natural that, as soon as this technology became reasonably stable, musical applications started to emerge.

% State clearly how you aim to deal with this problem. 
% Limit the scope of your study. 
% Sketch out how the thesis is structured to achieve your aim.

@@

>>>>

\documentclass{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\title{Sound Synthesis}
\author{Carlos Tarjano}

@@

\maketitle

\begin{abstract}

\end{abstract}

{\bf Keywords:}

\section{Introduction}
% Tell the reader the problem you are tackling in this project. 
% State clearly how you aim to deal with this problem. 
% Limit the scope of your study. 
% Sketch out how the thesis is structured to achieve your aim.

@@

\section{Bibliographic Review}

\subsection{Sound Representation}
frequency domain, one hot encoding, spectrogram

\subsection{Computer Graphics}
Bezier, splines, some raster, image rotation

\subsection{Sound synthesis}

\section{Methodology}

\section{Results}

\section{Discussion + Conclusion}

\section{References}
